---
title: "Level3"
output: word_document
date: "2024-06-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Task 1: Predictive Modeling
Build a regression model to predict the
aggregate rating of a restaurant based on
available features.
Split the dataset into training and testing sets
and evaluate the model's performance using
appropriate metrics.
Experiment with different algorithms (e.g.,
linear regression, decision trees, random
forest) and compare their performance.

```{r}
train_index<-sample(1:120,0.7*120)
x_train<-df$Encode_Has_Table_Booking[train_index]
y_train<-df$Aggregate.rating[train_index]
x_test<-df$Encode_Has_Table_Booking[-train_index]
y_test<-df$Aggregate.rating[-train_index]
df_train<-data.frame(x=x_train,y=y_train)
df_test<-data.frame(x=x_test,y=y_test)
lm_model<-function(df_train){
   beta1<-sum((df_train$x-mean(df_train$x))*(df_train$y-mean(df_train$y)))/sum((df_train$x-mean(df_train$x))^2)
 beta0<-mean(df_train$y)-beta1*mean(df_train$x)
 return(c(x1=beta0,y1=beta1))
}
library(dplyr)
ans<-lm_model(df_train)
print("Slope and Intercept From Linear Regression Model")
ans
lr_predict<-function(ans,df_test)
{
 y_pred<-ans["x1"]+ans["y1"]*df_test$x
 return(data.frame(pred=y_pred))
}
ans1<-lr_predict(ans,df_test)
print("Prediction Of Aggregate Rating based On Features")
glimpse(head(ans1))

#Performance Evaluation
mse<-mean((df_test$y-ans1$pred)^2)
mse<-sqrt(mse)
print("The Evaluated Performance Metrices based on Root Mean Square Error")
mse

```
Task 2: Customer Preference Analysis
Analyze the relationship between the type of
cuisine and the restaurant's rating.
Identify the most popular cuisines among
customers based on the number of votes.
Determine if there are any specific cuisines
that tend to receive higher ratings.
```{r}
ans<-head(df)
ggplot(data =ans)+geom_bar(mapping = aes(x=Cuisines,y=Aggregate.rating),stat = "identity")

ggplot(data =ans)+geom_boxplot(mapping = aes(x=Cuisines,y=Aggregate.rating))
print("Most Popular Cuisines")
df %>% filter(Votes==max(Votes)) %>% summarise(Cuisines)
print("Specific Cuisines to receive high Ratings")
df %>% filter(Aggregate.rating==max(Aggregate.rating)) %>% reframe(Cuisines)
```

Task 3: Data Visualization
Create visualizations to represent the distribution
of ratings using different charts (histogram, bar
plot, etc.).
Compare the average ratings of different cuisines
or cities using appropriate visualizations.
Visualize the relationship between various
features and the target variable to gain insights.

```{r}
hist(df$Aggregate.rating,main = "Distribution Of Ratings",xlab = "Rating",ylab = "Frequency")
barplot(df$Aggregate.rating,main = "Distribution Of Ratings",xlab = "Rating",ylab = "Frequency")
plot(df$Aggregate.rating,main = "Distribution Of Ratings",xlab = "Rating",ylab = "Frequency")

avg_rate_diff_cuisine<-head(df %>% group_by(Cuisines) %>% summarise(avg_rating=mean(Aggregate.rating)),4)

library(ggplot2)
ggplot(data=avg_rate_diff_cuisine,mapping=aes(x=Cuisines,y=avg_rating))+geom_bar(stat="identity")+labs(title = "Comparison of Ratings Vs Cuisines")

avg_rate_diff_city<-head(df %>% group_by(City) %>% summarise(avg_rating=mean(Aggregate.rating)),4)

ggplot(data=avg_rate_diff_city,mapping=aes(x=City,y=avg_rating))+geom_bar(stat="identity")+labs(title = "Comparison of Ratings Vs City")
ggplot(data=df)+geom_boxplot(mapping=aes(x=Cuisines,y=Aggregate.rating))+coord_cartesian(xlim = c(0,3))
```

