---
title: "Level1"
output: html_document
date: "2024-06-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Level 1
Task 1: Data Exploration and Preprocessing
Explore the dataset and identify the number
of rows and columns.
Check for missing values in each column and
handle them accordingly.
Perform data type conversion if necessary.
Analyze the distribution of the target variable
("Aggregate rating") and identify any class
imbalances.
```{r}
df=read.csv('E:/Virtual_Intern/Dataset .csv')
print("Number of Rows:")
print(nrow(df))
print("Number of Columns:")
print(ncol(df))
print("Missing Values:")
print(sum(is.na(df)))
AggregateRating=df$Aggregate.rating
hist(AggregateRating)
```
Task 2:Descriptive Analysis
Calculate basic statistical measures (mean,
median, standard deviation, etc.) for numerical
columns.
Explore the distribution of categorical
variables like "Country Code,
" "City,
" and
"Cuisines.
"
Identify the top cuisines and cities with the
highest number of restaurants.

```{r}
print("Mean,Median and Standard Deviation Of Various Numerical Features")
mean(df$Restaurant.ID,na.rm=TRUE)
median(df$Restaurant.ID,na.rm=TRUE)
sd(df$Restaurant.ID,na.rm=TRUE)
mean(df$Country.Code,na.rm=TRUE)
median(df$Country.Code,na.rm=TRUE)
sd(df$Country.Code,na.rm=TRUE)
mean(df$Longitude,na.rm=TRUE)
median(df$Longitude,na.rm=TRUE)
sd(df$Longitude,na.rm=TRUE)
mean(df$Latitude,na.rm=TRUE)
median(df$Latitude,na.rm=TRUE)
sd(df$Latitude,na.rm=TRUE)
mean(df$Average.Cost.for.two,na.rm=TRUE)
median(df$Average.Cost.for.two,na.rm=TRUE)
sd(df$Average.Cost.for.two,na.rm=TRUE)
mean(df$Price.range,na.rm=TRUE)
median(df$Price.range,na.rm=TRUE)
sd(df$Price.range,na.rm=TRUE)
mean(df$Aggregate.rating,na.rm=TRUE)
median(df$Aggregate.rating,na.rm=TRUE)
sd(df$Aggregate.rating,na.rm=TRUE)
mean(df$Votes,na.rm=TRUE)
median(df$Votes,na.rm=TRUE)
sd(df$Votes,na.rm=TRUE)
library(ggplot2)
x1<-head(df)
ggplot()+
geom_bar(data=x1,mapping = aes(x=Country.Code))+labs(title = "Distribution Of Categorical Variables")
ggplot()+
geom_bar(data=x1,mapping = aes(x=City))+labs(title = "Distribution Of Categorical Variables")
ggplot()+
geom_bar(data=x1,mapping = aes(x=Cuisines))+labs(title = "Distribution Of Categorical Variables")
library(dplyr)
ans<-df %>% group_by(City) %>% summarize(count=n())
print("Highest Number Of Restaurants with Top Cities")
head(arrange(ans,desc(count)),10)
ans1<-df %>% group_by(Cuisines) %>% summarize(count=n())
print("Highest Number Of Restaurants with Top Cuisines")
head(arrange(ans1,desc(count)),10)
```
Task 3: Geospatial Analysis
Visualize the locations of restaurants on a
map using latitude and longitude
information.
Analyze the distribution of restaurants
across different cities or countries.
Determine if there is any correlation
between the restaurant's location and its
rating.
```{r}
library(leaflet)
map<-leaflet(df) %>% addTiles() %>% setView(lng = mean(df$Longitude),lat = mean(df$Latitude),zoom=4)
map<-map %>% addCircleMarkers(lng = ~Longitude,lat = ~Latitude,popup=~paste("Locality:",`Locality`),radius = 3,color = 'red',stroke = FALSE,fillOpacity = 0.6)
library(htmlwidgets)
print("Mapping is Saved")
saveWidget(map,'restaurant.html',selfcontained = TRUE)

group_Restaurant<- df %>% group_by(Restaurant.ID)
Group_City<- group_Restaurant %>% group_by(City) %>% summarize(Count=n())
top_Restaurant<-head(Group_City)

ggplot(data = top_Restaurant)+geom_bar(mapping=aes(x=City,y=Count),stat = "identity")+labs(title = "Distribution Of Restaurants")

category_to_numeric<-as.numeric(factor(df$Locality))
cor_val<-cor(category_to_numeric,df$Aggregate.rating)
if(cor_val<0){
  print("Datas(Locality and Aggregate Rating) are -vely Correlated")
}else{
  print("Datas(Locality and Aggregate Rating) are Positively Correlated")
}

```