---
title: "Level2"
output:
  word_document: default
  html_document: default
  pdf_document: default
date: "2024-06-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Task 1: Table Booking and Online Delivery
Determine the percentage of restaurants that
offer table booking and online delivery.
Compare the average ratings of restaurants
with table booking and those without.
Analyze the availability of online delivery
among restaurants with different price ranges.
```{r}
library(base)
t1<-df$Has.Online.delivery
Online_percent<-prop.table(table(t1))
Table_booking<-prop.table(table(df$Has.Table.booking))
print("Online Delivery")
a1<-Online_percent['Yes']*100
a1
print("Table Booking")
a2<-Table_booking['Yes']*100
a2
avg_rating<-aggregate(Aggregate.rating~Has.Table.booking,data=df,FUN = mean)
print("Average Rating Of Restaurants")
avg_rating
Online_delivery_availability<-aggregate(Has.Online.delivery~Price.range,data=df,FUN=function(x) mean(x=='Yes')*100)

print("Availability Of Online Delivery with Different Price Ranges")
Online_delivery_availability
```

Task 2: Price Range Analysis
Determine the most common price range
among all the restaurants.
Calculate the average rating for each price
range.
Identify the color that represents the highest
average rating among different price ranges.
```{r}
tab<-table(df$Price.range)
print("Most Common Price Range")
names(tab[which.max(tab)])
print("Average Rating for each Price Range")
library(dplyr)
avg_rating_diff_price_range<-df %>% group_by(price_range=df$Price.range) %>% summarize( Average_Rating=mean(Aggregate.rating))

print("Average Rating based On Different Price Range")
avg_rating_diff_price_range

highest_avg_rating<-avg_rating_diff_price_range %>% filter(Average_Rating==max(Average_Rating))
color_highest_price_avg_rate<-df %>% group_by(Rating.color) %>% filter(Price.range==highest_avg_rating$price_range) %>% summarise(count=n())
print("Color that represents the highest
average rating among different price ranges")
color_highest_price_avg_rate
```
Task 3: Feature Engineering
Extract additional features from the existing
columns, such as the length of the restaurant
name or address.
Create new features like "Has Table Booking"
or "Has Online Delivery" by encoding
categorical variables.

```{r}
df['Length_of_Restaurant_name']<-nchar(df$Restaurant.Name)
df['Length_of_Restaurant_Address']<-nchar(df$Address)
print("Length of Restaurant Address")
head(df$Length_of_Restaurant_Address)
print("Length of Restaurant Name")
head(df$Length_of_Restaurant_name)
df['Encode_Has_Table_Booking']=as.numeric(factor(df$Has.Table.booking))
print("Encoded Restaurant_Has_Table_Booking")
head(df$Encode_Has_Table_Booking)
df['Encode_Has_Online_Delivery']=as.numeric(factor(df$Has.Online.delivery))
print("Encoded Restaurant_Has_Online_Delivery")
head(df$Encode_Has_Online_Delivery)
```

