---
title: "Level1"
output:
  word_document: default
  pdf_document: default
date: "2024-05-28"
---

Level 1
Task 1: Data Exploration and Preprocessing
Explore the dataset and identify the number
of rows and columns.
Check for missing values in each column and
handle them accordingly.
Perform data type conversion if necessary.
Analyze the distribution of the target variable
("Aggregate rating") and identify any class
imbalances.
```{r}
df=read.csv('E:/Virtual_Intern/Dataset .csv')
print("Number of Rows:")
print(nrow(df))
print("Number of Columns:")
print(ncol(df))
print("Missing Values:")
print(sum(is.na(df)))
AggregateRating=df$Aggregate.rating
hist(AggregateRating)
```
Task 2:Descriptive Analysis
Calculate basic statistical measures (mean,
median, standard deviation, etc.) for numerical
columns.
Explore the distribution of categorical
variables like "Country Code,
" "City,
" and
"Cuisines.
"
Identify the top cuisines and cities with the
highest number of restaurants.

```{r}
print("Mean,Median and Standard Deviation Of Various Numerical Features")
mean(df$Restaurant.ID,na.rm=TRUE)
median(df$Restaurant.ID,na.rm=TRUE)
sd(df$Restaurant.ID,na.rm=TRUE)
mean(df$Country.Code,na.rm=TRUE)
median(df$Country.Code,na.rm=TRUE)
sd(df$Country.Code,na.rm=TRUE)
mean(df$Longitude,na.rm=TRUE)
median(df$Longitude,na.rm=TRUE)
sd(df$Longitude,na.rm=TRUE)
mean(df$Latitude,na.rm=TRUE)
median(df$Latitude,na.rm=TRUE)
sd(df$Latitude,na.rm=TRUE)
mean(df$Average.Cost.for.two,na.rm=TRUE)
median(df$Average.Cost.for.two,na.rm=TRUE)
sd(df$Average.Cost.for.two,na.rm=TRUE)
mean(df$Price.range,na.rm=TRUE)
median(df$Price.range,na.rm=TRUE)
sd(df$Price.range,na.rm=TRUE)
mean(df$Aggregate.rating,na.rm=TRUE)
median(df$Aggregate.rating,na.rm=TRUE)
sd(df$Aggregate.rating,na.rm=TRUE)
mean(df$Votes,na.rm=TRUE)
median(df$Votes,na.rm=TRUE)
sd(df$Votes,na.rm=TRUE)
library(ggplot2)
x1<-head(df)
ggplot()+
geom_bar(data=x1,mapping = aes(x=Country.Code))+labs(title = "Distribution Of Categorical Variables")
ggplot()+
geom_bar(data=x1,mapping = aes(x=City))+labs(title = "Distribution Of Categorical Variables")
ggplot()+
geom_bar(data=x1,mapping = aes(x=Cuisines))+labs(title = "Distribution Of Categorical Variables")
library(dplyr)
ans<-df %>% group_by(City) %>% summarize(count=n())
print("Highest Number Of Restaurants with Top Cities")
head(arrange(ans,desc(count)),10)
ans1<-df %>% group_by(Cuisines) %>% summarize(count=n())
print("Highest Number Of Restaurants with Top Cuisines")
head(arrange(ans1,desc(count)),10)
```
Task 3: Geospatial Analysis
Visualize the locations of restaurants on a
map using latitude and longitude
information.
Analyze the distribution of restaurants
across different cities or countries.
Determine if there is any correlation
between the restaurant's location and its
rating.
```{r}
library(leaflet)
map<-leaflet(df) %>% addTiles() %>% setView(lng = mean(df$Longitude),lat = mean(df$Latitude),zoom=4)
map<-map %>% addCircleMarkers(lng = ~Longitude,lat = ~Latitude,popup=~paste("Locality:",`Locality`),radius = 3,color = 'red',stroke = FALSE,fillOpacity = 0.6)
library(htmlwidgets)

saveWidget(map,'restaurant.html',selfcontained = TRUE)
print("Map is Saved")
group_Restaurant<- df %>% group_by(Restaurant.ID)
Group_City<- group_Restaurant %>% group_by(City) %>% summarize(Count=n())
top_Restaurant<-head(Group_City)

ggplot(data = top_Restaurant)+geom_bar(mapping=aes(x=City,y=Count),stat = "identity")+labs(title = "Distribution Of Restaurants")

category_to_numeric<-as.numeric(factor(df$Locality))
cor_val<-cor(category_to_numeric,df$Aggregate.rating)
if(cor_val<0){
  print("Datas(Locality and Aggregate Rating) are -vely Correlated")
}else{
  print("Datas(Locality and Aggregate Rating) are Positively Correlated")
}

```
Level 2:
Task 1: Table Booking and Online Delivery
Determine the percentage of restaurants that
offer table booking and online delivery.
Compare the average ratings of restaurants
with table booking and those without.
Analyze the availability of online delivery
among restaurants with different price ranges.
```{r}
library(base)
t1<-df$Has.Online.delivery
Online_percent<-prop.table(table(t1))
Table_booking<-prop.table(table(df$Has.Table.booking))
print("Online Delivery")
a1<-Online_percent['Yes']*100
a1
print("Table Booking")
a2<-Table_booking['Yes']*100
a2
avg_rating<-aggregate(Aggregate.rating~Has.Table.booking,data=df,FUN = mean)
print("Average Rating Of Restaurants")
avg_rating
Online_delivery_availability<-aggregate(Has.Online.delivery~Price.range,data=df,FUN=function(x) mean(x=='Yes')*100)

print("Availability Of Online Delivery with Different Price Ranges")
Online_delivery_availability
```
Task 2: Price Range Analysis
Determine the most common price range
among all the restaurants.
Calculate the average rating for each price
range.
Identify the color that represents the highest
average rating among different price ranges.
```{r}
tab<-table(df$Price.range)
print("Most Common Price Range")
names(tab[which.max(tab)])
print("Average Rating for each Price Range")
library(dplyr)
avg_rating_diff_price_range<-df %>% group_by(price_range=df$Price.range) %>% summarize( Average_Rating=mean(Aggregate.rating))

avg_rating_diff_price_range

highest_avg_rating<-avg_rating_diff_price_range %>% filter(Average_Rating==max(Average_Rating))

color_highest_price_avg_rate<-df %>% group_by(Rating.color) %>% filter(Price.range==highest_avg_rating$price_range) %>% summarise(count=n())
print("Color that represents the highest
average rating among different price ranges")
color_highest_price_avg_rate
```
Task 3: Feature Engineering
Extract additional features from the existing
columns, such as the length of the restaurant
name or address.
Create new features like "Has Table Booking"
or "Has Online Delivery" by encoding
categorical variables.

```{r}
df['Length_of_Restaurant_name']<-nchar(df$Restaurant.Name)
df['Length_of_Restaurant_Address']<-nchar(df$Address)
print("Length of Restaurant Address")
head(df$Length_of_Restaurant_Address)
print("Length of Restaurant Name")
head(df$Length_of_Restaurant_name)
df['Encode_Has_Table_Booking']=as.numeric(factor(df$Has.Table.booking))
print("Encoded Restaurant_Has_Table_Booking")
head(df$Encode_Has_Table_Booking)
df['Encode_Has_Online_Delivery']=as.numeric(factor(df$Has.Online.delivery))
print("Encoded Restaurant_Has_Online_Delivery")
head(df$Encode_Has_Online_Delivery)
```
Level 3:
Task 1: Predictive Modeling
Build a regression model to predict the
aggregate rating of a restaurant based on
available features.
Split the dataset into training and testing sets
and evaluate the model's performance using
appropriate metrics.
Experiment with different algorithms (e.g.,
linear regression, decision trees, random
forest) and compare their performance.
```{r}
train_index<-sample(1:120,0.7*120)
x_train<-df$Encode_Has_Table_Booking[train_index]
y_train<-df$Aggregate.rating[train_index]
x_test<-df$Encode_Has_Table_Booking[-train_index]
y_test<-df$Aggregate.rating[-train_index]
df_train<-data.frame(x=x_train,y=y_train)
df_test<-data.frame(x=x_test,y=y_test)
lm_model<-function(df_train){
   beta1<-sum((df_train$x-mean(df_train$x))*(df_train$y-mean(df_train$y)))/sum((df_train$x-mean(df_train$x))^2)
 beta0<-mean(df_train$y)-beta1*mean(df_train$x)
 return(c(x1=beta0,y1=beta1))
}
ans<-lm_model(df_train)
print("Slope and Intercept From Linear Regression Model")
ans
lr_predict<-function(ans,df_test)
{
 y_pred<-ans["x1"]+ans["y1"]*df_test$x
 return(data.frame(pred=y_pred))
}
ans1<-lr_predict(ans,df_test)

print("Prediction Of Aggregate Rating based On Features")
glimpse(head(ans1))

#Performance Evaluation
mse<-mean((df_test$y-ans1$pred)^2)
mse<-sqrt(mse)

print("The Evaluated Performance Metrices based on Root Mean Square Error")
mse

```

Task 2: Customer Preference Analysis
Analyze the relationship between the type of
cuisine and the restaurant's rating.
Identify the most popular cuisines among
customers based on the number of votes.
Determine if there are any specific cuisines
that tend to receive higher ratings.
```{r}
ans<-head(df)
ggplot(data =ans)+geom_bar(mapping = aes(x=Cuisines,y=Aggregate.rating),stat = "identity")

ggplot(data =ans)+geom_boxplot(mapping = aes(x=Cuisines,y=Aggregate.rating))
print("Most Popular Cuisines")
df %>% filter(Votes==max(Votes)) %>% summarise(Cuisines)
print("Specific Cuisines to receive high Ratings")
df %>% filter(Aggregate.rating==max(Aggregate.rating)) %>% reframe(Cuisines)
```
Task 3: Data Visualization
Create visualizations to represent the distribution
of ratings using different charts (histogram, bar
plot, etc.).
Compare the average ratings of different cuisines
or cities using appropriate visualizations.
Visualize the relationship between various
features and the target variable to gain insights.

```{r}
hist(df$Aggregate.rating,main = "Distribution Of Ratings",xlab = "Rating",ylab = "Frequency")
barplot(df$Aggregate.rating,main = "Distribution Of Ratings",xlab = "Rating",ylab = "Frequency")
plot(df$Aggregate.rating,main = "Distribution Of Ratings",xlab = "Rating",ylab = "Frequency")

avg_rate_diff_cuisine<-head(df %>% group_by(Cuisines) %>% summarise(avg_rating=mean(Aggregate.rating)),4)

library(ggplot2)
ggplot(data=avg_rate_diff_cuisine,mapping=aes(x=Cuisines,y=avg_rating))+geom_bar(stat="identity")+labs(title = "Comparison of Ratings Vs Cuisines")

avg_rate_diff_city<-head(df %>% group_by(City) %>% summarise(avg_rating=mean(Aggregate.rating)),4)

ggplot(data=avg_rate_diff_city,mapping=aes(x=City,y=avg_rating))+geom_bar(stat="identity")+labs(title = "Comparison of Ratings Vs City")
ggplot(data=df)+geom_boxplot(mapping=aes(x=Cuisines,y=Aggregate.rating))+coord_cartesian(xlim = c(0,3))
```